---
title: 'Photosynthetic carbon uptake correlates with cell protein content during lipid accumulation in the microalgae Chlorella vulgaris NIES 227'
author: "Paul Chambonniere"
date: "29/04/2021"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE,warning = FALSE)
```

# Scope

This markdown document aims at showing the results associated to the pubication "Photosynthetic carbon uptake correlates with cell protein content during lipid accumulation in the microalgae Chlorella vulgaris NIES 227".

# Load functions and packages
```{r Code preparation, echo = FALSE}
# Loading packages
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggtern))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(wesanderson))
suppressPackageStartupMessages(library(viridis))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(ggsci))
suppressPackageStartupMessages(library(scales))


# Loading functions

source('o2cell_light_local_interpol.R',echo=TRUE)

```



```{r Theme creation, echo=FALSE}
# Creation of a ggplot theme, idea provided by https://benjaminlouis-stat.fr/en/blog/2020-05-21-astuces-ggplot-rmarkdown/)

base_size <- 20

theme_paul <- theme_bw(base_size = base_size) %+replace%
  theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0.5),
      # Zone où se situe le graphique
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85), face = "bold"),
      axis.text = element_text(size = rel(0.70), face = "bold"),
      axis.line = element_line(color = "black", arrow = arrow(length = unit(0.5, "lines"), type = "closed")),
      # La légende
      # legend.title = element_text(size = rel(0.85), face = "bold"),
      legend.title = element_blank(),
      legend.text = element_text(size = rel(0.70), face = "bold"),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      legend.box.margin = margin(0.1, 0.05, 0.1 , 0.05),
      legend.box.spacing = unit(3, units = "pt"),
      # Les étiquettes dans le cas d'un facetting
      strip.background = element_rect(fill = "#17252D", color = "#17252D"),
      strip.text = element_text(size = rel(0.85), face = "bold", color = "white", margin = margin(5,0,5,0))
    )


my_color_fill <- viridis(4, alpha = 1, begin = 0, end = 1, direction = 1, option = "D")
my_color_fill_highNumber <- viridis(6, alpha = 1, begin = 0, end = 1, direction = 1, option = "D")
my_color_manual <- viridis(12, alpha = 1, begin = 0, end = 1, direction = 1, option = "D")

theme_paul_highColourFill <- list(theme_paul,scale_fill_manual(values =  my_color_fill_highNumber),scale_color_manual(values =  my_color_manual))
theme_paul <- list(theme_paul,scale_fill_manual(values =  my_color_fill),scale_color_manual(values =  my_color_manual))

```

# Data Import

## Main data import

```{r, echo = TRUE}
# Data Import:

results_jumbo <- read_excel("Results_Jumbo.xlsx" , sheet = "General", col_names = TRUE,
                    n_max = Inf)
  date <- unlist(results_jumbo$Date,recursive = TRUE , use.names = FALSE)
  dryweight <- unlist(results_jumbo$`Dry weight (g/L)`,recursive = TRUE , use.names = FALSE) #g/L
    dryweight_error_plus <- 1.08*dryweight # 8% error considered as evaluated by Chambonniere et al based on Bechet et al
    dryweight_error_minus <- 0.92*dryweight
  factor_dilution_TOC <- unlist(results_jumbo$`Factor Dilution TOC`,recursive = TRUE , use.names = FALSE)
  toc_dryweight <- factor_dilution_TOC*dryweight
  toc_toc <- unlist(results_jumbo$`TOC biomass test solution (mg/L)`,recursive = TRUE , use.names = FALSE) # mg/L
  toc_tn <- unlist(results_jumbo$`TN biomass test solution (mg/L, as measured)`,recursive = TRUE , use.names = FALSE) # mg/L
  cell_count <- unlist(results_jumbo$`Total cell count (/mL)`,recursive = TRUE , use.names = FALSE) #number/mL
    cell_count1  <- unlist(results_jumbo$`Measured cell count (/mL)`,recursive = TRUE , use.names = FALSE)*unlist(results_jumbo$`Pre dilution factor`,recursive = TRUE , use.names = FALSE)*unlist(results_jumbo$`Dilution factor` ,recursive = TRUE , use.names = FALSE)
    cell_count2  <- unlist(results_jumbo$`Measured cell count 2 (/mL)`,recursive = TRUE , use.names = FALSE)*unlist(results_jumbo$`Pre dilution factor`,recursive = TRUE , use.names = FALSE)*unlist(results_jumbo$`Dilution factor`,recursive = TRUE , use.names = FALSE)
    cell_count_error_plus <- apply(matrix(c(cell_count1,cell_count2),ncol=2),1,max,na.rm = TRUE)
    cell_count_error_plus <- apply(matrix(c(1.15*cell_count,cell_count_error_plus),ncol=2),1,max,na.rm = TRUE) # 15% error is applied as a minimum based on side study from all duplicate values I collected (15% is the std deviation of the distribution for rel errors calculated as (max - min)/mean)
    cell_count_error_minus <- apply(matrix(c(cell_count1,cell_count2),ncol=2),1,min,na.rm = TRUE)
    cell_count_error_minus <- apply(matrix(c(0.85*cell_count,cell_count_error_minus),ncol=2),1,min,na.rm = TRUE)
  lipids <- unlist(results_jumbo$`Total lipids  (% g FAME/g DW)`,recursive = TRUE , use.names = FALSE)
  error_lipids <- unlist(results_jumbo$`Error (% g FAME/g DW)`,recursive = TRUE , use.names = FALSE)
  # We assume 11% error when value is 0 due to no replicate
  lipid_simplicate <- error_lipids == 0
  lipid_simplicate[is.na(lipid_simplicate) == 1 ] <- FALSE
  error_lipids[lipid_simplicate] <- 0.11*lipids[lipid_simplicate]
  sugars <- unlist(results_jumbo$`Starch (%, g/gTSS)`,recursive = TRUE , use.names = FALSE)
  error_sugars <- unlist(results_jumbo$`Error (%, g/g DW)`,recursive = TRUE , use.names = FALSE)
  # We assume 20% error when value is 0 due to no replicate
  sugars_simplicate <- error_sugars == 0
  sugars_simplicate[is.na(sugars_simplicate) == 1 ] <- FALSE
  error_sugars[sugars_simplicate] <- 0.20*sugars[sugars_simplicate]
  
  
  # Treatment of data:
  day <- as.double((date - date[1])/(24*3600))
  date <- as.Date(date)
  
  # Dryweight for day 5 is replaced by interpolation for both framing dates (since abnormally low, and scale error was likely). Same needs to be done for dryweight in TOC
  dryweight[4] <- dryweight[3] + (dryweight[5] - dryweight[3])/(day[5] - day[3])*(day[4]-day[3])
  toc_dryweight[4] <- 50/50 * dryweight[4]
  # 2 evident outliers for specific toc: not any reason to exclude them though
  
  # Vector created for data analysis of TOC-TN
  toc_specific <- toc_toc/toc_dryweight/1000 #g/g
  tn_specific <- toc_tn/toc_dryweight/1000 #g/g
  tn_supernatant = results_jumbo$`TN supernatant`*results_jumbo$`Dilution factor supernatant` #g/g
  factor_protein <- 5.04 # Based on Templeton et al. (2015)
  protein_content <- factor_protein*tn_specific*100
  
  day_harvest_1 = 39
  day_harvest_2 = 84
  day_harvest_3 = 124
  
  date_harvest_1 = as.Date("2021-03-22") 
  date_harvest_2 = as.Date("2021-05-06")
  date_harvest_3 = as.Date("2021-06-15")
  
  
  # Data treatment for O2 cell data analysis
  V_cell = 5.51*10^(-6) # m3
  OD_880_o2cell = results_jumbo$OD880
  dry_weight_o2cell = results_jumbo$`Dry weight (g/L)`/results_jumbo$`Dilution tested (Factor)`
  sigma_683_o2cell <- 100*results_jumbo$OD683*log(10)/dry_weight_o2cell # m2/kg
  I_cell_software_1 = results_jumbo$`Light intensity 1`
  I_cell_software_2 = results_jumbo$`Light intensity 2`
  I_cell_software_3 = results_jumbo$`Light intensity 3`
  
  # Respiration coefficient (positive for negative contribution) in g O2/g/s
  k_d_resp_1 = -results_jumbo$`Respiration 1 (mgO2/L/min)`/1000/60/dry_weight_o2cell
  dk_d_resp_1 = -results_jumbo$`Error respiration 1`/1000/60/dry_weight_o2cell
  k_d_resp_2 = -results_jumbo$`Respiration 2 (mgO2/L/min)`/1000/60/dry_weight_o2cell
  dk_d_resp_2 = -results_jumbo$`Error respiration 2`/1000/60/dry_weight_o2cell
  k_d_resp_3 = -results_jumbo$`Respiration 3 (mgO2/L/min)`/1000/60/dry_weight_o2cell
  dk_d_resp_3 = -results_jumbo$`Error respiration 3`/1000/60/dry_weight_o2cell
  
  # Total O2 production in the O2 cell (g O2/s)
  P_O2_1 = results_jumbo$`Productivity 1 (mgO2/L/min)`/60*V_cell
  dP_O2_1 = results_jumbo$`Error productivity 1`/60*V_cell
  P_O2_2 = results_jumbo$`Productivity 2 (mgO2/L/min)`/60*V_cell
  dP_O2_2 = results_jumbo$`Error productivity 2`/60*V_cell
  P_O2_3 = results_jumbo$`Productivity 3 (mgO2/L/min)`/60*V_cell
  dP_O2_3 = results_jumbo$`Error productivity 3`/60*V_cell
  o2cell_test = as.numeric(!is.na(results_jumbo$`Dilution tested (Factor)`))
  
  # Cell quotas
  lipid_quota_cell = (lipids/100)*dryweight/cell_count/1000 # g/cell
  sugars_quota_cell = (sugars/100)*dryweight/cell_count/1000 # g/cell
  protein_quota_cell = (protein_content/100)*dryweight/cell_count/1000 # g/cell
  mass_cell = dryweight/cell_count/1000 # g/cell
  
  
  # Compilation in a single data frame for later analysis
  
  data_jumbo <- data.frame(date = date , day = day , 
                           dryWeight = dryweight , dryWeightErrorPlus = dryweight_error_plus , dryWeightErrorMinus = dryweight_error_minus,
                           cellCount = cell_count , cellCountErrorPlus = cell_count_error_plus, cellCountErrorMinus = cell_count_error_minus,
                           tnSupernatant = tn_supernatant ,
                           o2CellTest = o2cell_test, OD880O2Cell = OD_880_o2cell, sigma683O2Cell = sigma_683_o2cell, dryWeightO2Cell = dry_weight_o2cell, ICellSoftware1 = I_cell_software_1, ICellSoftware2 = I_cell_software_2, ICellSoftware3 = I_cell_software_3, kdResp1 = k_d_resp_1, kdResp2 = k_d_resp_2, kdResp3 = k_d_resp_3, PO21 = P_O2_1, PO22 = P_O2_2, PO23 = P_O2_3, dkdResp1 = dk_d_resp_1, dkdResp2 = dk_d_resp_2, dkdResp3 = dk_d_resp_3, dPO21 = dP_O2_1, dPO22 = dP_O2_2, dPO23 = dP_O2_3,
                           tocSpecific = toc_specific , tnSpecific = tn_specific , factorDilutionTOC = factor_dilution_TOC ,
                           lipids = lipids , errorLipids = error_lipids ,
                           sugars = sugars , errorSugars = error_sugars ,
                           proteinContent = protein_content,
                           lipidQuotaCell = lipid_quota_cell,
                           sugarsQuotaCell = sugars_quota_cell,
                           proteinQuotaCell = protein_quota_cell,
                           massCell = mass_cell
                           )
  
  # Limitation of data to up to the third harvest (since the culture was not thoroughly monitored after this):
  
  data_jumbo <- subset(data_jumbo,day <= day_harvest_3 )
  
```


## Photosynthetic data creation
```{r, echo = TRUE, message = FALSE}


PO2_light_spec_1 <- c()
PO2_light_spec_2 <- c()
PO2_light_spec_3 <- c()

q_light_absorbed_O2cell <- c()
m_algae_O2cell <- c()
n_algae_O2cell <- c()

n_mesh <- 25



for (i in 1:nrow(data_jumbo)){
  if (data_jumbo$o2CellTest[i] == 1){
    
    I_algae <- o2cell_light_local_interpol(n = n_mesh, I_software = 100 , OD_880 = data_jumbo$OD880O2Cell[i])
    # This function creates a light field array of the oximetric cell
    
    # We now create an elementary volume array in accordance with the light field array
    dV <- array(NA,dim = c(n_mesh,n_mesh,n_mesh + 1))
      
      for (i_dV in 1:(dim(dV)[1])){
        for (j_dV in 1:(dim(dV)[2])){
          for (k_dV in 1:(dim(dV)[3]-1)){
            dV[i_dV,j_dV,k_dV] <- I_algae$rcoordinates[i_dV]*
              (I_algae$rcoordinates[i_dV+1]-I_algae$rcoordinates[i_dV])*
              (I_algae$tetacoordinates[j_dV+1]-I_algae$tetacoordinates[j_dV])*
              (I_algae$zcoordinates[k_dV+1]-I_algae$zcoordinates[k_dV]) 
          }
        }
      }
      
      for (i_dV in 1:(dim(dV)[1])){
        for (j_dV in 1:(dim(dV)[2])){
          dV[i_dV,j_dV,n_mesh+1] <- I_algae$rcoordinates[i_dV]*
            (I_algae$rcoordinates[i_dV+1]-I_algae$rcoordinates[i_dV])*
            (I_algae$tetacoordinates[j_dV+1]-I_algae$tetacoordinates[j_dV])*
            (I_algae$zcoordinates[n_mesh+1]-I_algae$zcoordinates[n_mesh])
        }
      }
    
    
    q_light_used = sum(data_jumbo$sigma683O2Cell[i]*data_jumbo$dryWeightO2Cell[i]*(I_algae$I_cell*dV),na.rm = TRUE) # Rate of light used by the microalgae in the O2 cell (mumol/s)
    m_algae = data_jumbo$dryWeightO2Cell[i]*V_cell*1000 # total mass of algae in the O2 cell (g DW) 
    n_cell = data_jumbo$cellCount[i]*1000*data_jumbo$dryWeightO2Cell[i]/data_jumbo$dryWeight[i]*V_cell*1000 # Number of algae cells in the O2 cell (NA)
    
    
    PO2_light_spec_1 <- c(PO2_light_spec_1,(data_jumbo$PO21[i] + data_jumbo$kdResp1[i]*m_algae)/q_light_used)
    PO2_light_spec_2 <- c(PO2_light_spec_2,(data_jumbo$PO22[i] + data_jumbo$kdResp2[i]*m_algae)/q_light_used)
    PO2_light_spec_3 <- c(PO2_light_spec_3,(data_jumbo$PO23[i] + data_jumbo$kdResp3[i]*m_algae)/q_light_used)
    
    q_light_absorbed_O2cell <- c(q_light_absorbed_O2cell,q_light_used)
    m_algae_O2cell <- c(m_algae_O2cell,m_algae)
    n_algae_O2cell <- c(n_algae_O2cell,n_cell)
      
  }else{
    
    PO2_light_spec_1 <- c(PO2_light_spec_1,NA)
    PO2_light_spec_2 <- c(PO2_light_spec_2,NA)
    PO2_light_spec_3 <- c(PO2_light_spec_3,NA)
    
    q_light_absorbed_O2cell <- c(q_light_absorbed_O2cell,NA)
    m_algae_O2cell <- c(m_algae_O2cell,NA)
    n_algae_O2cell <- c(n_algae_O2cell,NA)    
  }
}

data_jumbo$qLightAbsorbedO2cell = q_light_absorbed_O2cell
data_jumbo$mAlgaeO2cell = m_algae_O2cell
data_jumbo$nAlgaeO2cell = n_algae_O2cell

data_jumbo$PO2LightSpec = rowMeans(matrix(c(PO2_light_spec_1 , PO2_light_spec_2 , PO2_light_spec_3),ncol = 3),na.rm = TRUE)

PO2_gross = rowMeans(matrix(c(data_jumbo$PO21 + data_jumbo$kdResp1*data_jumbo$mAlgaeO2cell, 
                             data_jumbo$PO22 + data_jumbo$kdResp2*data_jumbo$mAlgaeO2cell,
                             data_jumbo$PO23 + data_jumbo$kdResp3*data_jumbo$mAlgaeO2cell),ncol = 3),na.rm = TRUE)

data_jumbo$PO2Gross <- PO2_gross
```

## Calculation of uncertainties

Uncertainties are computed based on experimental uncertainty and error propagation principles assuming variables are independent. Further hypothese for calculation are detailed below.
```{r, echo = FALSE}
# Uncertainty on cell protein quota
  # HYP 1: No uncertainty on protein factor
  # HYP 2: Uncertainty on TN measurement : +/- 2.4% relative error (literature, see manuscript)
  # HYP 3: F dilution: +/- 1% relative error (estimate from lab analysis)

delta_protein_content <- data_jumbo$proteinContent*sqrt((2.4/100)^2 + ((data_jumbo$dryWeightErrorPlus - data_jumbo$dryWeightErrorPlus)/(2*data_jumbo$dryWeight))^2)
data_jumbo$deltaProteinContent <- delta_protein_content

delta_protein_quota_cell <- 
  data_jumbo$proteinQuotaCell*sqrt((2.4/100)^2 + 
                            sqrt((1/100)^2 +
                                   ((data_jumbo$cellCountErrorPlus-data_jumbo$cellCountErrorMinus)/(2*data_jumbo$cellCount))^2))
data_jumbo$deltaProteinQuotaCell <- delta_protein_quota_cell


# Uncertainty on cell lipid quota

delta_lipid_quota_cell <- data_jumbo$lipidQuotaCell*
  sqrt((data_jumbo$errorLipids/data_jumbo$lipids)^2 + 
        ((data_jumbo$dryWeightErrorPlus-data_jumbo$dryWeightErrorMinus)/(2*data_jumbo$dryWeight))^2 +
         ((data_jumbo$cellCountErrorPlus - data_jumbo$cellCountErrorMinus)/(2*data_jumbo$cellCount))^2)
data_jumbo$deltaLipidQuotaCell <- delta_lipid_quota_cell

# Uncertainty on cell CHO quota

delta_sugars_quota_cell <- data_jumbo$sugarsQuotaCell*
  sqrt((data_jumbo$errorSugars/data_jumbo$sugars)^2 + 
        ((data_jumbo$dryWeightErrorPlus-data_jumbo$dryWeightErrorMinus)/(2*data_jumbo$dryWeight))^2 +
         ((data_jumbo$cellCountErrorPlus - data_jumbo$cellCountErrorMinus)/(2*data_jumbo$cellCount))^2)
data_jumbo$deltaSugarsQuotaCell <- delta_sugars_quota_cell

# Uncertainty on light specific O2 productivity
  # HYP 1: Uncertainty on P gross is taken as the max minus the min of the difference of PO2_gross accounting for uncertainty (i.e. [max{i}(PO2_i_gross + dPO2_i_gross) - min{i}(PO2_i_gross - dPO2_i_gross)]/2
  # HYP 2: idem for respiration
  # Hyp 3: we assume a conservative 20% uncertainty on light absorbed, maybe to be reviewed
delta_Q_light_relative = 0.2


delta_PO2_net <- (apply(matrix(c(data_jumbo$PO21 + data_jumbo$dPO21,data_jumbo$PO22 + data_jumbo$dPO22,data_jumbo$PO23 + data_jumbo$dPO23),
                                ncol = 3),1,max,na.rm = TRUE) - 
                      apply(matrix(c(data_jumbo$PO21 - data_jumbo$dPO21,data_jumbo$PO22 - data_jumbo$dPO22,data_jumbo$PO23 - data_jumbo$dPO23),
                                ncol = 3),1,min,na.rm = TRUE))/2

delta_kd_resp <- (apply(matrix(c(data_jumbo$kdResp1 + data_jumbo$dkdResp1,data_jumbo$kdResp2 + data_jumbo$dkdResp2,data_jumbo$kdResp3 + data_jumbo$dkdResp3),ncol = 3),1,max,na.rm = TRUE) -
                    apply(matrix(c(data_jumbo$kdResp1 - data_jumbo$dkdResp1,data_jumbo$kdResp2 - data_jumbo$dkdResp2,data_jumbo$kdResp3 - data_jumbo$dkdResp3),ncol = 3),1,min,na.rm = TRUE))/2


delta_PO2_gross <- sqrt(delta_PO2_net^2 + (data_jumbo$mAlgaeO2cell*delta_kd_resp)^2)

delta_PO2_light_spec <- sqrt((delta_PO2_gross/data_jumbo$PO2Gross)^2 + delta_Q_light_relative^2)*data_jumbo$PO2LightSpec
data_jumbo$deltaPO2LightSpec <- delta_PO2_light_spec


```

# Results

## Biomass monitoring
```{r, echo = FALSE}
# Data for day 1 is removed since it was obtained from the undiluted stock solution
data_jumbo$dryWeight[1] <- NA
data_jumbo$dryWeightErrorPlus[1] <- NA
data_jumbo$dryWeightErrorMinus[1] <- NA

data_jumbo$cellCount[1] <- NA
data_jumbo$cellCountErrorPlus[1] <- NA
data_jumbo$cellCountErrorMinus[1] <- NA

# Clear outliers for cell count are also removed to not hinder analysis. It is believed were encountered with a pipette at the start of the study.
data_jumbo$cellCount[4] <- NA
data_jumbo$cellCountErrorPlus[4] <- NA
data_jumbo$cellCountErrorMinus[4] <- NA
data_jumbo$cellCount[6] <- NA
data_jumbo$cellCountErrorPlus[6] <- NA
data_jumbo$cellCountErrorMinus[6] <- NA
data_jumbo$cellCount[9] <- NA
data_jumbo$cellCountErrorPlus[9] <- NA
data_jumbo$cellCountErrorMinus[9] <- NA


plot_dryWeight <- ggplot(data_jumbo,
                  aes(x = date , y = dryWeight)) +
  geom_point(shape = 18, size = 3, stroke = 1.5, fill = 'black') +
  geom_errorbar(aes(ymin = dryWeightErrorMinus, ymax = dryWeightErrorPlus),width = 1) +
  labs(y = expression(bold(atop("Biomass concentration", paste("(g DW·L"^"-1",")"))))) +
  coord_cartesian(xlim = c(as.Date("2021-02-01"),date_harvest_3 + 1), ylim = c(0,7)) + 
  geom_vline(xintercept = date_harvest_1,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_2,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_3,linetype = "twodash",size = 1) +
  theme_paul_highColourFill +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())

plot_cellCount <- ggplot(data_jumbo,
                  aes(x = date , y = cellCount*1000)) +
  geom_point(shape = 18, size = 3, stroke = 1.5, fill = 'blue') +
  geom_errorbar(aes(ymin = cellCountErrorMinus*1000, ymax = cellCountErrorPlus*1000),width = 1) +
  labs(x = "Day of culture", y = expression(bold(atop("Cell count", paste("(cell·L"^"-1",")"))))) +
  coord_cartesian(xlim = c(as.Date("2021-02-01"),date_harvest_3 + 1)) +
  scale_y_log10() +
  geom_vline(xintercept = date_harvest_1,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_2,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_3,linetype = "twodash",size = 1) +
  scale_x_date(labels = date_format("%m-%Y")) +
  theme_paul_highColourFill + 
  theme(axis.title.x = element_blank())


```

```{r, echo = FALSE, fig.width=10, fig.height=5}

plot_dryWeight
plot_cellCount


nested_biomass <- plot_dryWeight + plot_cellCount + plot_layout(nrow = 2)
nested_biomass

```


## Internal quota

### Calculation of internal quota for defined period
```{r, echo = TRUE}
dateEndExpo = as.Date("2021-03-02")
data_jumbo$proteinContent[data_jumbo$date <= dateEndExpo]
data_jumbo$lipids[data_jumbo$date <= dateEndExpo]
data_jumbo$sugars[data_jumbo$date <= dateEndExpo]

mean(data_jumbo$proteinContent[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
mean(data_jumbo$lipids[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
mean(data_jumbo$sugars[data_jumbo$date <= dateEndExpo],na.rm = TRUE)

sd(data_jumbo$proteinContent[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
sd(data_jumbo$lipids[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
sd(data_jumbo$sugars[data_jumbo$date <= dateEndExpo],na.rm = TRUE)



data_jumbo$proteinQuotaCell[data_jumbo$date <= dateEndExpo]
data_jumbo$lipidQuotaCell[data_jumbo$date <= dateEndExpo]
data_jumbo$sugarsQuotaCell[data_jumbo$date <= dateEndExpo]

mean(data_jumbo$proteinQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
mean(data_jumbo$lipidQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
mean(data_jumbo$sugarsQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)

sd(data_jumbo$proteinQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
sd(data_jumbo$lipidQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
sd(data_jumbo$sugarsQuotaCell[data_jumbo$date <= dateEndExpo],na.rm = TRUE)


min(data_jumbo$proteinContent,na.rm = TRUE)
max(data_jumbo$lipids,na.rm = TRUE)


```

### Internal quota vs time
#### Mass quota

```{r, echo = TRUE}


## Mass quota
# Creation of another data frame for the ggplot formatting of the cell quotas
functional_pool = 100 - (data_jumbo$lipids + data_jumbo$sugars + data_jumbo$proteinContent)
ind_remove = which(is.na(functional_pool))

days_remove = data_jumbo$day[ind_remove]


category = c(rep("Lipids",length(data_jumbo$lipids)),rep("Carbohydrate",length(data_jumbo$sugars)),rep("Proteins",length(data_jumbo$proteinContent)),rep("Functional pool",length(functional_pool)))
data_quota = data.frame(quotas = c(data_jumbo$lipids,data_jumbo$sugars,data_jumbo$proteinContent,functional_pool), 
                        day = c(rep(data_jumbo$day,4)),date = c(rep(data_jumbo$date,4)),
                        quotaCategory = category)


data_quota_reduced <- data_quota[!data_quota$day %in% days_remove,]

```



#### Cell quota (and relative partition)
```{r, echo = TRUE}

## Cell quota

functional_pool_cell = data_jumbo$massCell - (data_jumbo$lipidQuotaCell + data_jumbo$sugarsQuotaCell + data_jumbo$proteinQuotaCell)
functional_pool_cell = pmax(functional_pool_cell,0)
ind_remove = which(is.na(functional_pool_cell))

days_remove = data_jumbo$day[ind_remove]


category = c(rep("Total FAMEs",length(data_jumbo$lipidQuotaCell)),rep("Total carbohydrates",length(data_jumbo$sugarsQuotaCell)),rep("Proteins",length(data_jumbo$proteinQuotaCell)),rep("Functional compartment",length(functional_pool_cell)))
data_quota_cell = data.frame(quotas = c(data_jumbo$lipidQuotaCell,data_jumbo$sugarsQuotaCell,data_jumbo$proteinQuotaCell,functional_pool_cell), 
                        quotaError = c(data_jumbo$deltaLipidQuotaCell,data_jumbo$deltaSugarsQuotaCell,data_jumbo$deltaProteinQuotaCell,functional_pool_cell),
                        day = c(rep(data_jumbo$day,4)),date = c(rep(data_jumbo$date,4)),
                        quotaCategory = category)


data_quota_cell_reduced <- data_quota_cell[!data_quota_cell$day %in% days_remove,]

```

```{r, echo = FALSE}
# Area chart of quotas

data_quota_cell_reduced$quotaCategory2 <- factor(data_quota_cell_reduced$quotaCategory,levels = c("Proteins","Functional compartment","Total carbohydrates","Total FAMEs"))

plot_meta_state_date_relative <- ggplot(data = data_quota_cell_reduced,
                          aes(x = date, y = quotas)) +
  geom_area(aes( fill = quotaCategory2), position = "fill") +
  coord_cartesian(xlim = c(as.Date("2021-02-01"),date_harvest_3 + 1)) +
  geom_vline(xintercept = date_harvest_1,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_2,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_3,linetype = "twodash",size = 1) +
  labs(x = "", y = expression(bold(atop("Cell relative composition", paste("(mg·(mg DW)"^"-1",")"))))) +
  scale_x_date(labels = date_format("%m-%Y")) +
  theme_paul  +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) +
  scale_fill_manual(values = c(my_color_fill[3],my_color_fill[1],my_color_fill[2],my_color_fill[4]) )

  data_quota_cell_reduced_noFunctionalPool <- data_quota_cell_reduced[data_quota_cell_reduced$quotaCategory2 != "Functional compartment",]

plot_meta_state_date_cell <-
  ggplot(data = data_quota_cell_reduced_noFunctionalPool,
         aes(x = date, y = quotas, fill = quotaCategory2)) +
  coord_cartesian(xlim = c(as.Date("2021-02-01"),date_harvest_3 + 1)) +
  geom_errorbar(aes(ymin = quotas - quotaError,ymax = quotas + quotaError),width = 5) + 
  geom_point(shape = 21, size = 4, stroke = 1, alpha = 0.75 , postion = "jitter")+
  geom_vline(xintercept = date_harvest_1,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_2,linetype = "twodash",size = 1) +
  geom_vline(xintercept = date_harvest_3,linetype = "twodash",size = 1) +
  scale_y_log10() + 
  labs(x = "", y = expression(bold(atop("Cell composition", paste("(mg·cell"^"-1",")"))))) +
  scale_x_date(labels = date_format("%m-%Y")) +
  theme_paul  +
  scale_fill_manual(values = c(my_color_fill[3],my_color_fill[2],my_color_fill[4]))
  
```

```{r, echo=FALSE, fig.height=5, fig.width=10}
plot_meta_state_date_cell
plot_meta_state_date_relative

plot_meta_state <- plot_meta_state_date_relative + plot_meta_state_date_cell + plot_layout(nrow = 2)

```


## Biomass photosynthesis productivity



### Ternary plots of PI prod

```{r, echo = FALSE}

tern_PO2LightSpec <-
  ggtern(data = subset(data_jumbo,!is.na(PO2LightSpec)),aes(y=lipids/100,x=sugars/100,z=proteinContent/100)) + 
      geom_point(aes(fill=PO2LightSpec),color="black",shape=21,size=5,alpha = 0.9,show.legend = TRUE) + 
      theme_paul + 
      theme(legend.position=c(0,1),
            legend.justification=c(0,1)) + 
    scale_colour_viridis_c(option = "D") + 
    scale_fill_viridis_c(option = "D",trans = "log",breaks=c(2*10^(-7),5*10^(-7),2*10^(-6),1*10^(-6))) +
      labs( title = expression(bold(atop(paste("Light specifc rate of O"[2]," production"), paste("(g O"[2],"·",mu,"mol"^"-1",")")))),
            colour = "gO2/g dw/s",
            x = "",
            xarrow = "Relative carbohydrate content (%)",
            y = "",
            yarrow = "Relative FAMEs content (%)",
            z = "",
            zarrow = "Relative Protein content (%)")  +
      theme(legend.background = element_rect(fill = FALSE), tern.axis.arrow = element_line(size = 3) , 
            tern.axis.arrow.text.T = element_text(vjust = 0),
            tern.axis.arrow.text.L = element_text(vjust = 0),
            tern.axis.arrow.text.R = element_text(vjust = 1),
            ) +
      theme_showarrows()


```

```{r, echo = FALSE, fig.height=6,fig.width=6}
tern_PO2LightSpec

mean(data_jumbo$PO2LightSpec[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
sd(data_jumbo$PO2LightSpec[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
min(data_jumbo$PO2LightSpec[data_jumbo$date <= dateEndExpo],na.rm = TRUE)
max(data_jumbo$PO2LightSpec[data_jumbo$date <= dateEndExpo],na.rm = TRUE)

min(data_jumbo$PO2LightSpec,na.rm = TRUE)


```


# Modelling


## Rate of photosynthetic O2 production 
### Fitting of protein cell quota dependent coefficient to light specific rate of O2 production:

We determined log transformed light specific O2 rate of production to be well approximated by a linear function of log(qp/qp_min) (the use of the log transformation can be justified by the large differences that may unbalance the fitting).

We obtain a function of light specific O2 rate of production in the form: lambda*(qp_mock/qp_min)^(alpha) where lambda and alpha are constant determined through linear regression.

```{r, echo = TRUE}
qp_min <- min(data_jumbo$proteinQuotaCell,na.rm = TRUE)
df_linearFit <- data.frame(x = log10(data_jumbo$proteinQuotaCell/qp_min), y = log10(data_jumbo$PO2LightSpec),
                           lipidQuotaCell = data_jumbo$lipidQuotaCell, lipids = data_jumbo$lipids)

df_linearFit <- df_linearFit[is.na(rowSums(df_linearFit)) == 0,] # Removing lines with NA values so that the residuals can be analyzed.

linearModel <- lm(y ~ x, data = df_linearFit )
summary(linearModel)
plot(linearModel)

str(linearModel)

df_linearFit$residuals <- linearModel$residuals

ggplot(data = df_linearFit, aes(x = lipids, y = residuals)) +
  geom_point() +
  theme_paul

lambda <- as.numeric(10^(linearModel$coefficients[1]))
alpha <- as.numeric(linearModel$coefficients[2])


# lambda
print(lambda)
# alpha
print(alpha)
# qp_min
print(qp_min)

qp_mock <- c(seq(from = qp_min/2, to = 10*qp_min,by = qp_min/10),seq(from = 11*qp_min,to = 2*10^(-11),length.out = 100 ))
PO2_mock <- lambda*(qp_mock/qp_min)^(alpha)
data_PO2_mock <- data.frame(qpMock = qp_mock,PO2Mock = PO2_mock)
```

```{r, echo = FALSE}
plot_PO2LightSpec_withFit <- ggplot(data_jumbo,aes(x = proteinQuotaCell , y = PO2LightSpec)) +
  geom_errorbar(aes(ymin = PO2LightSpec - deltaPO2LightSpec, ymax = PO2LightSpec + deltaPO2LightSpec),width = 10^(-1)) +
  geom_errorbar(aes(xmin = proteinQuotaCell - deltaProteinQuotaCell, xmax = proteinQuotaCell + deltaProteinQuotaCell ),width = 0.1,alpha = 0.5) +
  geom_point(shape = 21 , size = 4,fill = 'white',stroke = 1.5) +
  geom_line(data = data_PO2_mock, aes(x = qpMock, y = PO2Mock), size = 1) + 
  labs(x = expression(bold(paste("Protein cell quota (g Proteins·cell"^"-1",")"))), y = expression(bold(atop(paste("Light specifc rate of O"[2]," production"), paste("(g O"[2],"·",mu,"mol"^"-1",")"))))) +
  theme_paul + 
  scale_y_log10() + scale_x_log10()

```

```{r, echo = FALSE,fig.height=5,fig.width=7}
plot_PO2LightSpec_withFit

```


